Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-23 ICML-submission/from-weak-separability-to-strong-separability.tex
minor

In this section, we consider case when the examples are weakly linearly
separable. Throughout this section, we assume without loss of generality that
all examples lie in the unit ball $\B(\zero,1) \subseteq \R^d$.\footnote{Instead of
working with feature vector $x_t$ we can work with normalized feature vectors
$\widehat{x}_t = \frac{x_t}{\norm{x_t}}$. It can be easily checked that if
$(x_1,y_1), (x_2,y_2), \dots, (x_T,y_T)$ are weakly linearly separable with
margin $\gamma$ and $\norm{x_t} \le R$ for all $t$, then the normalized examples
$(\widehat{x}_1,y_1), (\widehat{x}_2,y_2), \dots, (\widehat{x}_T,y_T)$ are weakly
linearly separable with margin $\gamma/R$.} Note that
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
alone does not guarantee a finite mistake bound in this setting, as weak linear
separability does not imply strong linear separability.

We construct a positive definite kernel function $k(\cdot, \cdot)$ whose
corresponding feature map $\phi(\cdot)$ transforms any sequence of \emph{weakly}
linearly separable examples to \emph{strongly} linearly separable sequence of
examples. Specifically, $\phi$ has the property that if a set of labeled
examples in $\B(\zero,1)$ is weakly linearly separable with a margin $\gamma$, then
after applying $\phi$ the examples become strongly linearly separable with a
margin $\gamma'$ and their norms are bounded by $2$. The parameter $\gamma'$ is
a function of the old margin $\gamma$ and the number of classes $K$, and is
specified in \autoref{theorem:margin-transformation} below.

@@

%\begin{proof}[Proof sketch of Theorem~\ref{theorem:margin-transformation}]
%Since the examples $(x_1, y_1)$,  $\dots$, $(x_T, y_T)$ are weakly
%linearly separable with margin $\gamma$, there are vectors $w_1, w_2, \dots, w_K$
%satisfying \eqref{equation:weak-linear-separability-1} and
%\eqref{equation:weak-linear-separability-2}.

%Fix any $i \in \{1,2,\dots,K\}$. Consider the $K-1$ vectors $(w_i - w_j)/2$ for
%$j \in \{1,2,\dots,K\} \setminus \{i\}$. Note that the vectors have norm at most
%$1$. We consider two cases regarding the relationship between $\gamma_1$ and
%$\gamma_2$.

%\paragraph{Case 1: $\gamma_1 \geq \gamma_2$.} In this setting,
%Theorem~\ref{theorem:polynomial-approximation-1} implies that there exist a
%multivariate polynomial $p_i:\R^d \to \R$

%\begin{align*}
%\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{{2}/{\gamma}} \right\rceil \; ,
%\end{align*}
%such that all examples $x$ in $R_i^+$ (resp. $R_i^-$) satisfy $p_i(x) \geq 1/2$
%(resp. $p_i(x) \leq -1/2$).
%Therefore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$,
% and if $y_t \neq i$ then $p_i(x_t) \le -1/2$, and
%\begin{align*}
%&\norm{p_i}
%\\
%& \le
%\left[
%  188 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
%\right]^{
%  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil }{2}
%} \; . \\
%\end{align*}
%By \autoref{lemma:norm-bound}, there exists $c_i \in \ell_2$ such that
%$\ip{c_i}{\phi(x)}_{\ell_2} = p_i(x)$, and
%\begin{align*}
%&\norm{c_i}_{\ell_2}
%\\
%& \le
%\left[
%  376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
%\right]^{
%  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil}{2}
%} \; .
%\end{align*}
%Define vectors $u_i \in \ell_2$ as
%\begin{align*}
%u_i & =
%\frac{c_i/\sqrt{K}}{
%  \left[
%    376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
%  \right]^{
%    \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}{2}
%  }
%} \; . \\
%\end{align*}

%Then, $\norm{u_1}^2 + \norm{u_2}^2 + \dots + \norm{u_K}^2 \le 1$.
%Futhermore, for all $t=1,2,\dots,T$, $\ip{u_{y_t}}{x_t} \ge \gamma_1$
%and for all $j \in \{1,2,\dots,K\} \setminus \{y_t\}$,
%$\ip{u_j}{x_t} \le - \gamma_1$. In other words,
%$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
%strongly linearly separable with margin $\gamma_1 = \max\{\gamma_1, \gamma_2\}$.

%\paragraph{Case 2: $\gamma_1 \leq \gamma_2$.} Following the
%same idea as Case 1 and using Theorem~\ref{theorem:polynomial-approximation-1},
%we can show that
%$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
%strongly linearly separable with margin $\gamma_2 = \max\{\gamma_1, \gamma_2\}$.

%In summary, the examples are strongly
%linearly separable with margin $\gamma' = \max\{\gamma_1, \gamma_2\}$.
%Finally, observe that for any $t=1,2,\dots,T$,
%\[
%k(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
%\qedhere
%\]
%\end{proof}

>>>>

In this section, we consider the case when the examples are weakly linearly
separable. Throughout this section, we assume without loss of generality that
all examples lie in the unit ball $\B(\zero,1) \subseteq \R^d$.\footnote{Instead of
working with feature vector $x_t$ we can work with normalized feature vectors
$\widehat{x}_t = \frac{x_t}{\norm{x_t}}$. It can be easily checked that if
$(x_1,y_1), (x_2,y_2), \dots, (x_T,y_T)$ are weakly linearly separable with
margin $\gamma$ and $\norm{x_t} \le R$ for all $t$, then the normalized examples
$(\widehat{x}_1,y_1), (\widehat{x}_2,y_2), \dots, (\widehat{x}_T,y_T)$ are weakly
linearly separable with margin $\gamma/R$.} Note that
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
alone does not guarantee a finite mistake bound in this setting, as weak linear
separability does not imply strong linear separability.

We construct a positive definite kernel function $k(\cdot, \cdot)$ whose
corresponding feature map $\phi(\cdot)$ transforms any sequence of \emph{weakly}
linearly separable examples to \emph{strongly} linearly separable sequence of
examples. Specifically, $\phi$ has the property that if a set of labeled
examples in $\B(\zero,1)$ is weakly linearly separable with a margin $\gamma$, then
after applying $\phi$ the examples become strongly linearly separable with a
margin $\gamma'$ and their squared norms are bounded by $2$. The parameter $\gamma'$ is
a function of the old margin $\gamma$ and the number of classes $K$, and is
specified in \autoref{theorem:margin-transformation} below.

@@

\begin{proof}[Proof sketch of Theorem~\ref{theorem:margin-transformation}]
Since the examples $(x_1, y_1)$,  $\dots$, $(x_T, y_T)$ are weakly
linearly separable with margin $\gamma$, there are vectors $w_1, w_2, \dots, w_K$
satisfying \eqref{equation:weak-linear-separability-1} and
\eqref{equation:weak-linear-separability-2}.

Fix any $i \in \{1,2,\dots,K\}$. Consider the $K-1$ vectors $(w_i - w_j)/2$ for
$j \in \{1,2,\dots,K\} \setminus \{i\}$. Note that the vectors have norm at most
$1$. We consider two cases regarding the relationship between $\gamma_1$ and
$\gamma_2$.

\paragraph{Case 1: $\gamma_1 \geq \gamma_2$.} In this setting,
Theorem~\ref{theorem:polynomial-approximation-1} implies that there exist a
multivariate polynomial $p_i:\R^d \to \R$

\begin{align*}
\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{{2}/{\gamma}} \right\rceil \; ,
\end{align*}
such that all examples $x$ in $R_i^+$ (resp. $R_i^-$) satisfy $p_i(x) \geq 1/2$
(resp. $p_i(x) \leq -1/2$).
Therefore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$,
 and if $y_t \neq i$ then $p_i(x_t) \le -1/2$, and
\begin{align*}
&\norm{p_i}
\\
& \le
\left[
  188 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
\right]^{
  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil }{2}
} \; . \\
\end{align*}
By \autoref{lemma:norm-bound}, there exists $c_i \in \ell_2$ such that
$\ip{c_i}{\phi(x)}_{\ell_2} = p_i(x)$, and
\begin{align*}
&\norm{c_i}_{\ell_2}
\\
& \le
\left[
  376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
\right]^{
  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil}{2}
} \; .
\end{align*}
Define vectors $u_i \in \ell_2$ as
\begin{align*}
u_i & =
\frac{c_i/\sqrt{K}}{
  \left[
    376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
  \right]^{
    \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}{2}
  }
} \; . \\
\end{align*}

Then, $\norm{u_1}^2 + \norm{u_2}^2 + \dots + \norm{u_K}^2 \le 1$.
Futhermore, for all $t=1,2,\dots,T$, $\ip{u_{y_t}}{x_t} \ge \gamma_1$
and for all $j \in \{1,2,\dots,K\} \setminus \{y_t\}$,
$\ip{u_j}{x_t} \le - \gamma_1$. In other words,
$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
strongly linearly separable with margin $\gamma_1 = \max\{\gamma_1, \gamma_2\}$.

\paragraph{Case 2: $\gamma_1 \leq \gamma_2$.} Following the
same idea as Case 1 and using Theorem~\ref{theorem:polynomial-approximation-1},
we can show that
$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
strongly linearly separable with margin $\gamma_2 = \max\{\gamma_1, \gamma_2\}$.
%The proof for the case of $\gamma_1 < \gamma_2$
%is symmetric.

In summary, the examples are strongly
linearly separable with margin $\gamma' = \max\{\gamma_1, \gamma_2\}$.
Finally, observe that for any $t=1,2,\dots,T$,
\[
k(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
\qedhere
\]
\end{proof}

### 2019-01-23 ICML-submission/introduction.tex
Spell check introduction
minor

We study the problem of \textsc{Online Multiclass Linear Classification with
Bandit Feedback}~\citep{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
viewed as a repeated game between a learner and an adversary. At each timestep
$t$, the adversary chooses a labeled example $(x_t, y_t)$ and reveals $x_t\in
\R^d$ to the learner. Upon receiving $x_t$, the learner makes a prediction
$\widehat{y}_t$ and receives feedback. In contrast with the standard
full-information setting, where the feedback given is the correct label $y_t$,
here the feedback is only a binary indicator of whether the prediction was
correct or not. The protocol of the problem is formally stated below.

\begin{protocol}[h]
\caption{\textsc{Online Multiclass Linear Classification with Bandit Feedback}
\label{algorithm:game-protocol}}
\textbf{Require:} Number of classes $K$, number of rounds $T$. \\
\textbf{Require:} Inner product space $(V,\ip{\cdot}{\cdot})$. \\
\For{$t=1,2,\dots,T$}{
Adversary chooses example $(x_t, y_t) \in V \times \{1,2,\dots,K\}$ where $x_t$ is revealed to the learner.\\
Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.\\
Observe feedback $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$
}
\end{protocol}

@@

In this paper, we focus on the special case when the examples chosen by the
adversary lie in $\R^d$ and are linearly separable with a margin. We introduce
two notions of linear separability, \emph{weak} and \emph{strong}, formally
stated in \autoref{definition:linear-separability}. The standard notion of
multiclass linear separability~\citep{Crammer-Singer-2003} corresponds to the
weak linear separability. For multiclass classification with $K$ classes, weak
linear separability requires that all examples from the same class lie in an
intersection of $K-1$ halfspaces and all other examples lie in the complement of
the intersection of the halfspaces. Strong linear separability means that
examples from each class are separated from the remaining examples by a
\emph{single} hyperplane.

In the full-information feedback setting, it is well known
\citep{Crammer-Singer-2003} that if all examples have norm at most $R$ and are
weakly linearly separable with a margin $\gamma$, then the \textsc{Multiclass
Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes. It
is also known that any (possibly randomized) algorithm must make $\frac{1}{2}
\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. The
\textsc{Multiclass Perceptron} achieves an information-theoretically optimal
mistake bound, while being computationally and memory efficient.~\footnote{For
completeness, we present these folklore results along with their proofs in
Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
material.}

The bandit feedback setting, however, is much more challenging. For the case
when the examples are strongly linearly separable, to the best of our knowledge,
it is not known how to design an efficient algorithm with a finite mistake bound
before our work.~\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}
claimed that their Conservative OVA algorithm with PA-I update has a finite
mistake bound under the strong linear separability condition, their proof of
Theorem 2 is incorrect: first, their Theorem 2 implies a mistake upper bound of
$\frac{R}{\gamma}$ with sufficiently large $C$, which contradicts our lower
bound in Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
second, their Lemma 4 cannot be directly applied to the bandit setting, as the
algorithm only makes updates on a subset of the $w_i$'s.} We design a simple and
efficient algorithm
(Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})
that makes at most $O(K (R/\gamma)^2))$ mistakes in expectation. Its memory
complexity and per-round time complexity are both $O(dK)$. The algorithm can be
viewed as running $K$ copies of the \textsc{Binary Perceptron} algorithm, one
copy for each class. We prove that any (possibly randomized) algorithm must make
$\Omega(K (R/\gamma)^2))$ mistakes in the worst case. The extra $O(K)$
multiplicative factor in the mistake bound, as compared to the full-information
setting, is the price we pay for the bandit feedback, or more precisely, the
lack of full-information feedback.

For the case when the examples are weakly linearly separable, it was open for a
long time whether there exist \textit{efficient} algorithms with finite mistake
bound~\cite{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}.
Furthermore, in~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, they ask the question:
Is there \textit{any} algorithm with a finite mistake bound that has no explicit
dependence on the dimensionality of the feature vectors? We answer both
questions affirmatively by providing an efficient algorithm with finite
dimensionless mistake bound (Algorithm~\ref{algorithm:kernelized}).\footnote{An
in inefficient algorithm was given by~\cite{Daniely-Helbertal-2013}.}

@@

In Appendix~\ref{section:nearest-neighbor-algorithm}, we propose and analyze a
very different algorithm for weakly separable data. The algorithm is based on
the obvious idea that two points that are close enough must have the same label.

Finally, we study two questions related to the computational and
information-theoretic hardness of the problem. Any algorithm for the bandit
setting collects information in the form of so called \emph{strongly labeled}
and \emph{weakly labeled} examples. Strongly labeled examples are those for
which we know the class label. Weakly labeled example is an example for which we
know that class label can be anything except for a particular one class.
In Appendix~\ref{section:np-hardness-of-weak-labeling-problem}, we show that the offline
problem of finding a linear multiclass separator consistent with a set of
strongly and weakly labeled examples is NP-hard. In
Appendix~\ref{section:mistake-lower-bound-for-ignorant-algorithms}, we show that
any algorithm that uses only strongly-labeled examples and ignores weakly
labeled examples makes at least $\Omega\left( \left(1/(160 \gamma)\right)^{(d-2)/4} \right)$
mistakes.

>>>>

We study the problem of \textsc{Online Multiclass Linear Classification with
Bandit Feedback}~\citep{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
viewed as a repeated game between a learner and an adversary. At each
timestep $t$, the adversary chooses a labeled example $(x_t, y_t)$ and reveals $x_t\in \R^d$ to the learner.
Upon receiving $x_t$, the learner makes a prediction $\widehat{y}_t$ and receives feedback.
In contrast to the
standard full-information setting, where the feedback given is the correct label
$y_t$, here the feedback is only a binary indicator of whether the prediction
was correct or not. The protocol of the problem is formally stated below.

\begin{protocol}[h]
\caption{\textsc{Online Multiclass Linear Classification with Bandit Feedback}
\label{algorithm:game-protocol}}
\textbf{Require:} Number of classes $K$, number of rounds $T$.\\
\For{$t=1,2,\dots,T$}{
     Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.\\
     Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.\\
     Observe feedback
          $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$
%$z_t \in \{0,1\}$, \\ \qquad where $z_t = \begin{cases}
%0 & \text{if $\widehat y_t = y_t$,} \\
%1 & \text{if $\widehat y_t \neq y_t$.}
%\end{cases}$
}

\end{protocol}

@@

In this paper, we focus on the special case when the examples chosen by the
adversary lie in $\R^d$ and are linearly separable with a margin. We introduce
two notions of linear separability, \emph{weak} and \emph{strong}, formally
stated in
Definition~\ref{definition:weak-linear-separability}.
The standard notion of multiclass linear
separability~\citep{Crammer-Singer-2003} corresponds to the weak linear
separability. %For binary classification, the weak and strong separability are
%identical. However, they differ for multiclass classification with $K \ge 3$
%classes.
For multiclass classification with $K$ classes, weak linear
separability requires that all examples from the same class lie in an intersection of $K-1$ halfspaces and all other examples lie in the complement of
the intersection of the halfspaces. Strong linear separability means that
examples from each class are separated from the remaining examples by a
\emph{single} hyperplane.

In the full-information feedback setting, it is well known
\citep{Crammer-Singer-2003} that if all examples have norm at most $R$ and are
weakly linearly separable with a margin $\gamma$, then the \textsc{Multiclass
Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
%%%%%
It is also known that any (possibly randomized) algorithm must
make $\frac{1}{2} \left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the
worst case.
The \textsc{Multiclass Perceptron} achieves an
information-theoretically optimal mistake bound, while being
computationally and memory efficient.
~\footnote{
%%%%%
%These are folklore results.
For completeness, we present these
folklore
%%%%%
results along
with their proofs in Appendix~\ref{section:multiclass-perceptron-proofs} in the
supplementary material.}

The bandit feedback setting, however, is much more challenging. For the case
when the examples are strongly linearly separable, to the best of our knowledge,
it is not known how to design an efficient algorithm with a finite mistake bound
before our work.~\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}
claimed that their Conservative OVA algorithm with PA-I update has a finite
mistake bound under the strong linear separability condition, their
Theorem 2 is incorrect: first, their Theorem 2
implies a mistake upper bound of $\frac{R}{\gamma}$ with
sufficiently large $C$, which contradicts our lower
bound in Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
second, their Lemma 4 cannot be directly applied to the bandit
setting, as the algorithm only makes updates on a subset of the $w_i$'s.} We
design a simple and efficient algorithm
(Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})
that makes at most $O(K (R/\gamma)^2))$ mistakes in expectation. Its memory
complexity and per-round time complexity are both $O(dK)$. The algorithm can be
viewed as running $K$ copies of the \textsc{Binary Perceptron} algorithm, one
copy for each class. We prove that any (possibly randomized) algorithm must make
$\Omega(K (R/\gamma)^2))$ mistakes in the worst case. The extra $O(K)$
multiplicative factor the mistake bound, as compared to the full-information
setting, is the price we pay for the bandit feedback, or more precisely, the
lack of full-information feedback.

For the case when the examples are weakly linearly separable, it was open for a long
time whether there exist \textit{efficient} algorithms with finite mistake
bound~\cite{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}.
Furthermore, in~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, they ask the question:
is there \textit{any} algorithm with a finite mistake bound that has no explicit dependence
on the dimensionality of the feature vectors? We answer both questions affirmatively by
providing an efficient algorithm with finite dimensionless mistake bound
(Algorithm~\ref{algorithm:kernelized}).~\footnote{The second question was previously
answered by~\cite{Daniely-Helbertal-2013} with an inefficient algorithm.}

@@

### 2019-01-23 ICML-submission/related-work.tex
minor

The linear classification version of this problem is initially studied
by~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed two computationally
inefficient algorithms that work in the weakly linearly separable setting, one
with a mistake bound of 
$O(K^2 d \ln(d/\gamma))$,
the other with a
mistake bound of $\widetilde{O}((K^2/\gamma^2) \ln T)$. The latter result
was later improved by \citet{Daniely-Helbertal-2013}, which gives a
computationally inefficient algorithm with a mistake upper bound of
$\widetilde{O}(K/\gamma^2)$. 
In addition, the authors propose the
\textsc{Banditron} algorithm, a computationally efficient algorithm that has a
$O(T^{2/3})$ regret against the multiclass hinge loss in the general setting,
and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weakly linearly separable
setting.
In contrast to mild dependencies on the time horizon for mistake bounds of
computationally inefficient algorithms,
the polynomial dependence of \textsc{Banditron}'s mistake bound on the
time horizon is undesirable for problems with a long time horizon, in the
weakly linearly separable setting. One key open
question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can
design computationally efficient algorithms that achieve mistake bounds that
match or improve over those of inefficient algorithms. In this paper, we take a
step towards answering this question, showing that efficient algorithms with
mistake bounds quasipolynomial in $\frac 1 \gamma$ or quasipolynomial in $K$ can
be obtained.

>>>>

The linear classification version of this problem is initially studied
by~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed two computationally
inefficient algorithms that work in the weakly linearly separable setting, one
with a mistake bound of
$O(K^2 d \ln(d/\gamma))$,
the other with a
mistake bound of $\widetilde{O}((K^2/\gamma^2) \ln T)$. The latter result
was later improved by \citet{Daniely-Helbertal-2013}, which gives a
computationally inefficient algorithm with a mistake upper bound of
$\widetilde{O}(K/\gamma^2)$.
In addition, the authors propose the
\textsc{Banditron} algorithm, a computationally efficient algorithm that has a
$O(T^{2/3})$ regret against the multiclass hinge loss in the general setting,
and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weakly linearly separable
setting.
In contrast to mild dependencies on the time horizon for mistake bounds of
computationally inefficient algorithms,
the polynomial dependence of \textsc{Banditron}'s mistake bound on the
time horizon is undesirable for problems with a long time horizon, in the
weakly linearly separable setting. One key open
question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can
design computationally efficient algorithms that achieve mistake bounds that
match or improve over those of inefficient algorithms. In this paper, we take a
step towards answering this question, showing that efficient algorithms with
mistake bounds quasipolynomial in $1/\gamma$ (for constant $K$)
or quasipolynomial in $K$ (for constant $\gamma$) can be obtained.
